The process of retrieving schedule data from the Novasoftware web application

### 2016-04-18 paper/paper.tex
Cleaned up code and added a section in the paper about the GitHub README

	\subsection{Implementation}
	The implementation is hosted on the code sharing website GitHub at the following URL \url{https://github.com/johnrapp/novasoftware-schedule-parser}. You are free to download, modify and use the source code of this project without asking for permission. %Kanske ha en licens (kanske i GitHub istället)

	\subsubsection{Installation}
	%Kanske skriva det här i GitHub readmen så att den kan ändras
	The project requires Node.js on the running machine. Instructions for installing Node.js are found at the Node.js website \url{https://nodejs.org/en/download/}. %Kanske inte ta med pathen eftersom den kan ändras (bara https://nodejs.org)

@@

	\subsubsection{Usage}
	To run the program, open a terminal window and run the command\\
	\texttt{\$ node .}\\
	This will fetch all the Värmdö Gymnasium schedules and save them in the \texttt{schedules} directory.

>>>>

	\subsection{Implementation}
	The implementation is hosted on the code sharing website GitHub.com at the following URL: \url{https://github.com/johnrapp/novasoftware-schedule-parser}. You are free to download, modify and use the source code of this project without asking for permission.

	\subsubsection{Installation}
	The project requires Node.js on the running machine. Instructions for installing Node.js are found at the Node.js website \url{https://nodejs.org/en/download/}.

@@

	\subsubsection{Usage}
	To run the program, open a terminal window and run the command\\
	\texttt{\$ node .}\\
	This will fetch a selected set of schedules from Värmdö Gymnasium and save them in the \texttt{schedules} directory.

	\subsubsection{GitHub readme}
	More information about the provided implementation, as well as more thorough instructions may be found in the GitHub readme at \url{https://github.com/johnrapp/novasoftware-schedule-parser#readme}.
